\documentclass{beamer}

% Using your requested theme and color
\usetheme{Szeged}
\usecolortheme{beaver}

% --- Presentation Info ---
\title{Fibonacci Heap}
\subtitle{Outperforming Traditional Priority Queues}
\author{Pedro Marinho \and Miguel Mateus \and Tuomas Haapasalo}
\institute{University of Porto FEUP}
\date{March 23, 2026}

% Removes the small navigation icons at the bottom right
\setbeamertemplate{navigation symbols}{}
\setbeamertemplate{itemize items}[triangle]
\setbeamercolor{itemize item}{fg=black}
\begin{document}

% --- Title Slide ---
\begin{frame}
  \titlepage
\end{frame}

% --- 1. OUTLINE (1 dot) ---
\section{Overview}
\begin{frame}{Overview}
  % sections={2-8} ensures the "Outline" section doesn't list itself
  \tableofcontents[sections={2-8}]
\end{frame}

% --- AUTOMATED TOPIC TRANSITIONS ---
% Placing this here means it will automatically generate the grayed-out 
% transition slide for every section AFTER the Outline.
\AtBeginSection[]
{
  \begin{frame}{Overview}
    % currentsection highlights the active topic and fades the rest
    \tableofcontents[currentsection, sections={2-8}]
  \end{frame}
}

% --- 2. MOTIVATION (1 dot) ---
\section{Motivation}

\begin{frame}{Motivation}
  \begin{itemize}
    \item Efficient priority queues are a key problem in the context of graph algorithm design.
    \item There is an increased need for processing massive networks, but the repeated cost of updating node priorities poses a huge bottleneck!
    \item Demand for priority queue designs capable of extremely fast updates, but that can simultaneously keep other standard operations efficient.
  \end{itemize}
  
  \vspace{0.2cm}
  {\large \textcolor{darkred}{The $O(\log n)$ Bound}}
  
  \vspace{0.1cm}
  Currently, the effects of logarithmic slowness are much more visible! The number of edges in dense networks vastly exceeds the vertices, making priority updates the dominant computing cost \cite{fredman1987}.
\end{frame}


% --- 3. DATA STRUCTURE BASIS (7 dots) ---
\section{Data Structure Basis}
\begin{frame}{Data Structure Basis - Slide 1}\end{frame}
\begin{frame}{Data Structure Basis - Slide 2}\end{frame}
\begin{frame}{Data Structure Basis - Slide 3}\end{frame}


% --- 4. OPERATIONS (9 dots) ---
\section{Operations}
\begin{frame}{Operations - Slide 1}\end{frame}
\begin{frame}{Operations - Slide 2}\end{frame}
\begin{frame}{Operations - Slide 3}\end{frame}
\begin{frame}{Operations - Slide 4}\end{frame}
\begin{frame}{Operations - Slide 5}\end{frame}


% --- 5. APPLICATIONS (4 dots) ---
\section{Applications}
\begin{frame}{Applications - Slide 1}\end{frame}
\begin{frame}{Applications - Slide 2}\end{frame}
\begin{frame}{Applications - Slide 3}\end{frame}
\begin{frame}{Applications - Slide 4}\end{frame}

% --- 6. EXAMPLE (4 dots) ---
\section{Example}
\begin{frame}{Example - Slide 1}\end{frame}
\begin{frame}{Example - Slide 2}\end{frame}
\begin{frame}{Example - Slide 3}\end{frame}
\begin{frame}{Example - Slide 4}\end{frame}

% --- 7. CONCLUSIONS (2 dots) ---
\section{Conclusions}
\begin{frame}{Conclusions - Slide 1}\end{frame}
\begin{frame}{Conclusions - Slide 2}\end{frame}

% --- 8. REFERENCES (2 dots) ---
\section{References}
\begin{frame}{References}
  \begin{thebibliography}{99}
    
    \bibitem{fredman1987}
    Michael L. Fredman and Robert Endre Tarjan.
    \newblock Fibonacci heaps and their uses in improved network optimization algorithms.
    \newblock \emph{Journal of the ACM}, 34(3):596--615, 1987.
    
    \bibitem{cormen2009}
    Thomas H. Cormen, Charles E. Leiserson, Ronald L. Rivest, and Clifford Stein.
    \newblock \emph{Introduction to Algorithms, Third Edition}.
    \newblock MIT Press, 2009.
    
  \end{thebibliography}
\end{frame}
\end{document}